---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geocrs

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of geocrs is to provide tools for the basic validation and manipulation of coordinate reference system objects. It doesn't require a copy of PROJ, but does contain a partial copy of the latest PROJ database.

## Installation

You can install the development version of geocrs from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/geocrs")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(geocrs)

# create a CRS by guessing the input
as_crs(4326)
as_crs("EPSG:4326")
as_crs("+proj=longlat +datum=WGS84 +no_defs +type=crs")
```

Basic validation:

```{r, error=TRUE}
crs_code(0)
crs_code(4326, auth_name = "ESPG")
crs_json("wheee")
```

Basic conversion:

```{r}
as_crs_proj4(4326)
as_crs_wkt(4326, type = "WKT2:2019")
as_crs_json(4326)
```

